SOL Filamentary transport: update from joint AUG-TCV MST1 experiment

### 2018-01-25 Meetings/25ITPADivSOL/vianello_25itpadivsol.tex

\usepackage[style=nature,citestyle=authoryear-comp,defernumbers=true,maxnames=2,firstinits=true,
uniquename=init,backend=bibtex8,arxiv=abs,mcite]{biblatex}
\bibliography{biblio}
\renewcommand*{\bibfont}{\footnotesize}
\renewcommand*{\citesetup}{\footnotesize}
\usepackage[export]{adjustbox}
\makeatother
\mode<presentation>
\makeatletter
% add a macro that saves its argument
\newcommand{\footlineextra}[1]{\gdef\insertfootlineextra{#1}}
\newbox\footlineextrabox
% for reducing font on a single slide
\newcommand\Fontvi{\fontsize{8}{7.2}\selectfont}
\title{SOL Filamentary transport: update from joint AUG-TCV MST1 experiment}
\date{29 January 2018}
\author[N.Vianello]{presented by N. Vianello on behalf of  MST1-Topic 21
  scientific team}
\begin{document}
\tikzstyle{every picture}+=[remember picture]
\maketitle
\begin{frame}{Scientific team}
  \centering{
  Volker Naulin, Jiri Adamek, Matteo Agostini, Diogo Aguiam, Scott Allan, Matthias Bernert, Daniel Carralero Ortiz, 
Stefan Costea, Istvan Cziegler, Hugo De Oliveira, Joaquin Galdon-Quiroga, Gustavo Grenfell, Antti Hakola, 
Codrina Ionita-Schrittwieser, Heinz Isliker, Alexander Karpushov, Jernej Kovacic, Benoît Labit, Florian Laggner, Jens Madsen, 
Roberto Maurizio, Ken McClements, Fulvio Militello, Jeppe Miki Busk Olsen, Jens Juul Rasmussen, Timo Ravensbergen, Bernd Sebastian Schneider, Roman Schrittwieser, Jakub Seidl, Monica Spolaore, Christian Theiler, Cedric Kar-Wai Tsui, Kevin Verhaegh, Jose Vicente, 
Nickolas Walkden, Zhang Wei, Elisabeth Wolfrum, W. Vijvers}
j\end{frame}

@@

\begin{frame}{D$_{\alpha}$ tomography: work in progress}
\Fontvi
  \begin{columns}
    \begin{column}{0.5\textwidth}
      \includegraphics<1>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/Dalpha/inv_alfa_34104_2000}
      \includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/Dalpha/inv_alfa_34104_2700}
      \includegraphics<3>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/Dalpha/inv_alfa_34104_3100}
    \end{column}
    \begin{column}{0.5\textwidth}
      \begin{itemize}
        \item \alert{Preliminary} results from inversion tomography
          from calibrated D$_{\alpha}$ camera under the assumption of
          toroidally symmetric emission limited to the region outside
          the LCFS
        \item \emph{Simultaneous Algebraic Reconstruction Technique
            (SART) (A.H. Anderson and A.C.Kak,  Ultrasonic Imaging
            \textbf{6},  81 (1984))}
        \item As time evolves during the L-Mode ramp we observe
          D$_{\alpha}$ radiation moving from HFS towards the LFS
          common flux region
        \item \alert{This is consistent with JET observation in
            Horizontal target regime whenever shoulder is observed}
      \end{itemize}
    \end{column}
  \end{columns}
\end{frame}

>>>>

\usepackage[style=nature,citestyle=authoryear-comp,defernumbers=true,maxnames=2,firstinits=true,
uniquename=init,backend=bibtex8,arxiv=abs,mcite]{biblatex}
\bibliography{biblio}
\renewcommand*{\bibfont}{\footnotesize}
\renewcommand*{\citesetup}{\footnotesize}
\usepackage[export]{adjustbox}
\makeatother
\mode<presentation>
\makeatletter
% add a macro that saves its argument
\newcommand{\footlineextra}[1]{\gdef\insertfootlineextra{#1}}
\newbox\footlineextrabox
% for reducing font on a single slide
\newcommand\Fontvi{\fontsize{8}{7.2}\selectfont}
\title{SOL Filamentary transport: update from joint AUG-TCV MST1 experiment}
\date{29 January 2018}
\author[N.Vianello]{presented by N. Vianello on behalf of  MST1-Topic 21
  scientific team}
\begin{document}
\tikzstyle{every picture}+=[remember picture]
\maketitle
\begin{frame}{Scientific team}
  \centering{
  Volker Naulin, Matteo Agostini, Diogo Aguiam, Scott Allan, Matthias Bernert, Daniel Carralero Ortiz, 
Stefan Costea, Istvan Cziegler, Hugo De Oliveira, Joaquin Galdon-Quiroga, Gustavo Grenfell, Antti Hakola, 
Codrina Ionita-Schrittwieser, Heinz Isliker, Alexander Karpushov,
Jernej Kovacic, Benoît Labit, Bruce Lipschultz, 
Roberto Maurizio, Ken McClements, Fulvio Militello, Jeppe Miki Busk Olsen, Jens Juul Rasmussen, Timo Ravensbergen, Bernd Sebastian Schneider, Roman Schrittwieser, Jakub Seidl, Monica Spolaore, Christian Theiler, Cedric Kar-Wai Tsui, Kevin Verhaegh, Jose Vicente, 
Nickolas Walkden, Zhang Wei, Elisabeth Wolfrum, W. Vijvers}
j\end{frame}

@@

\begin{frame}{D$_{\alpha}$ tomography: work in progress}
\Fontvi
  \begin{columns}
    \begin{column}{0.5\textwidth}
      \includegraphics<1>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/Dalpha/inv_alfa_34104_2000}
      \includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/Dalpha/inv_alfa_34104_2700}
      \includegraphics<3>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/Dalpha/inv_alfa_34104_3100}
    \end{column}
    \begin{column}{0.5\textwidth}
      \begin{itemize}
        \item \alert{Preliminary} results from inversion tomography
          from calibrated D$_{\alpha}$ camera under the assumption of
          toroidally symmetric emission limited to the region outside
          the LCFS
        \item \emph{Simultaneous Algebraic Reconstruction Technique
            (SART) (A.H. Anderson and A.C.Kak,  Ultrasonic Imaging
            \textbf{6},  81 (1984))}
        \item<2-> As time evolves during the L-Mode ramp we observe
          D$_{\alpha}$ radiation moving from HFS towards the LFS
          common flux region
        \item<3-> \alert{This is consistent with JET observation in
            Horizontal target regime whenever shoulder is observed}
      \end{itemize}
    \end{column}
  \end{columns}
\end{frame}
